Supplemental Materials for: Meta-analytic approaches and effect sizes to account for ‘nuisance heterogeneity’ in comparative physiology

### 2021-07-23 supp.Rmd
Fixed naming of axes in places so consistent

In this supplement, we will demonstrate some of the principles we describe in our review paper. We'll show readers ways they can apply some of the 'new' effect sizes we describe to account for 'nuisance heterogeneity' in combination with multilevel meta-analytic models (MLMA) and/or multilevel meta-regression models. We realise that 'nuisance heterogeneity' may be a misnomer in some senses because such forms of heterogeneity may actually be the main interest of a given meta-analysis; in which case, multilevel meta-regressions are the way to go!

We will overview two different case studies. The first case study will show readers how to account for known drivers of effect heterogeneity in the effect size, followed by how we can fit a MLMA (intercept only) model to estimate an overall meta-analytic mean. We then show readers how to interpret this mean and associated heterogeneity. In the second case study, we use a common effect size metric and instead model the 'nuisance' heterogeneity using a multi-level meta-regression approach. We also focus on showing readers how to interpret effects from this model along with heterogeneity.

@@

Here, we will demonstrate how to analyse variation and differences in slopes between two groups. In this example, we will account for effects of known drivers of 'nuisance heterogeneity' at the level of the effect size. We use a case study by Pottier et al. *in review* which investigated the association between acclimation temperature, thermal tolerance and sex. We first demonstrate how to use meta-analytic approaches to investigate the variation in the relationship between acclimation temperature and thermal tolerance (i.e. variation in slope), and then demonstrate how to meta-analyse differences in slopes between two groups (i.e. sexes).

@@

We can see from above that the model estimates an overall meta-analytic mean as `r coef(model_CS1a_MLMA)` with a 95\% CI from `r model_CS1a_MLMA$ci.lb` to `r model_CS1a_MLMA$ci.ub`. In other words, for each degree variation in acclimation temperature, the heat tolerance of the animals included in this data set vary by `r coef(model_CS1a_MLMA)` degrees on average. 95\% of the time we expect the mean in repeated samples to fall between `r PI_CS1a_MLMA$cr.lb` and `r PI_CS1a_MLMA$cr.ub`.
Our prediction intervals suggest that heterogeneity is high, reflected in our $I_{total}^2$ estimate of `r I2_CS1a[1]*100`\%.  Approximately, `r I2_CS1a[2]*100`\% of the total heterogeneity is the result of differences between species, and `r I2_CS1a[3]*100`\% of the total heterogeneity is associated with the residuals. 
With this effect size (slope), the 'nuisance heterogeneity' is accounted for, to some extent, at the level of the effect size.

@@

We can now model these dosage effects to control for 'nuisance heterogeneity' and make the overall mean more interpretable. We'll first start by fitting and interpreting the coefficient just for the raw total dosage applied in a given study. To do this, we can now fit a multilevel meta-regression model as follows:

@@

```{r}
dat %>% 
  ggplot() + tm +
  geom_bar(aes(x = comparative_physiology_main_focus,
               fill = meta_analysis_self_described,
               y = ..count../sum(..count..)), width = 0.5,
           colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0)) +
  scale_fill_viridis_d() +
  labs(x = "main focus on comparative physiology",
       y = "number of papers",
       fill = "meta-analysis") 
```

@@

```{r}
dat %>% mutate(cont_moderator_variable_modelled = if_else(cont_moderator_variable_modelled == "", "N/A", cont_moderator_variable_modelled)) %>% 
  ggplot() + tm +
  geom_bar(aes(x = factor(cont_moderator_variable,levels=c("yes","no","unclear")),
               fill = cont_moderator_variable_modelled,
               y = ..count../sum(..count..)), width = 0.5,
           colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
  scale_fill_viridis_d() +
  labs(x = "Nuisance Heterogeneity?",
       y = "Proportion",
       fill = "Modeled Nuisance\n Heterogeneity?") 
```

>>>>

In this supplement, we will demonstrate some of the principles we describe in our review paper. We'll show readers ways they can apply some of the 'new' effect sizes we describe to account for nuisance heterogeneity in combination with multilevel meta-analytic models (MLMA) and/or multilevel meta-regression models. We realise that nuisance heterogeneity may be a misnomer in some senses because such forms of heterogeneity may actually be the main interest of a given meta-analysis; in which case, multilevel meta-regressions are the way to go!

We will overview two different case studies. The first case study will show readers how to account for known drivers of effect heterogeneity in the effect size, followed by how we can fit a MLMA (intercept only) model to estimate an overall meta-analytic mean. We then show readers how to interpret this mean and associated heterogeneity. In the second case study, we use a common effect size metric and instead model the nuisance heterogeneity using a multi-level meta-regression approach. We also focus on showing readers how to interpret effects from this model along with heterogeneity.

@@

Here, we will demonstrate how to analyse variation and differences in slopes between two groups. In this example, we will account for effects of known drivers of nuisance heterogeneity at the level of the effect size. We use a case study by Pottier et al. *in review* which investigated the association between acclimation temperature, thermal tolerance and sex. We first demonstrate how to use meta-analytic approaches to investigate the variation in the relationship between acclimation temperature and thermal tolerance (i.e. variation in slope), and then demonstrate how to meta-analyse differences in slopes between two groups (i.e. sexes).

@@

We can see from above that the model estimates an overall meta-analytic mean as `r coef(model_CS1a_MLMA)` with a 95\% CI from `r model_CS1a_MLMA$ci.lb` to `r model_CS1a_MLMA$ci.ub`. In other words, for each degree variation in acclimation temperature, the heat tolerance of the animals included in this data set vary by `r coef(model_CS1a_MLMA)` degrees on average. 95\% of the time we expect the mean in repeated samples to fall between `r PI_CS1a_MLMA$cr.lb` and `r PI_CS1a_MLMA$cr.ub`.
Our prediction intervals suggest that heterogeneity is high, reflected in our $I_{total}^2$ estimate of `r I2_CS1a[1]*100`\%.  Approximately, `r I2_CS1a[2]*100`\% of the total heterogeneity is the result of differences between species, and `r I2_CS1a[3]*100`\% of the total heterogeneity is associated with the residuals. 
With this effect size (slope), the nuisance heterogeneity is accounted for, to some extent, at the level of the effect size.

@@

We can now model these dosage effects to control for nuisance heterogeneity and make the overall mean more interpretable. We'll first start by fitting and interpreting the coefficient just for the raw total dosage applied in a given study. To do this, we can now fit a multilevel meta-regression model as follows:

@@

```{r}
dat %>% 
  ggplot() + tm +
  geom_bar(aes(x = comparative_physiology_main_focus,
               fill = meta_analysis_self_described,
               y = ..count../sum(..count..)), width = 0.5,
           colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0)) +
  scale_fill_viridis_d() +
  labs(x = "Main focus on comparative physiology?",
       y = "Frequency",
       fill = "Meta-analysis") 
```

@@

```{r}
dat %>% mutate(cont_moderator_variable_modelled = if_else(cont_moderator_variable_modelled == "", "N/A", cont_moderator_variable_modelled)) %>% 
  ggplot() + tm +
  geom_bar(aes(x = factor(cont_moderator_variable,levels=c("yes","no","unclear")),
               fill = cont_moderator_variable_modelled,
               y = ..count../sum(..count..)), width = 0.5,
           colour = text.colour, size = 0.5) +
  scale_y_continuous(expand=c(0,0), limits = c(0,1)) +
  scale_fill_viridis_d() +
  labs(x = "Nuisance Heterogeneity?",
       y = "Frequency",
       fill = "Modeled Nuisance\n Heterogeneity?") 
```
